Parsing Postfix log files

### 2007-12-23 doc/logparser-acronyms.tex
Improved other parsers review; it's more compare and contrast than it was. Picked Postfix Log Parser as the name. Added parser background section, introducing the rules/algorithm split. Hyperref doesn't work after upgrading to unstable, so it's disabled for now.
Replaced regexs with regexes.
Added some discussion of the similarity between the parser's rules/actions/algorithm split and Wood's Augmented Transition Networks.

@@

% I think this is better than having both regex and regexs in the acronym
% list.  Likewise for pids.
\newcommand{\regexs}{\regex{}s}
\newcommand{\pids}{\pid{}s}

@@

>>>>

\newacronym{PLP}{Postfix Log Parser}{description={
    Postfix Log Parser is the implementation of the algorithm described in
    this paper.
}}

@@

% I think this is better than having both regex and regexes in the acronym
% list.  Likewise for pids.
\newcommand{\regexes}{\regex{}es}
\newcommand{\pids}{\pid{}s}

@@

\newacronym{ATN}{Augmented Transition Networks}{description={
    Augmented Transition Networks are a tool used in Computational
    Linguistics; they are originally described in~\cite{atns} and further
    in~\cite{nlpip}.
}}

### 2007-12-23 doc/logparser.tex
Added some discussion of the similarity between the parser's rules/actions/algorithm split and Wood's Augmented Transition Networks.

>>>>

There is some similarity between the parser's design and William Wood's
\ATN{}~\cite{atns, nlpip}, a tool used in Computational Linguistics for
creating grammars to parse or generate sentences.  The resemblance between
\ATN{} and the parser is accidental, but it is interesting how two
apparently different approaches share an underlying separation of concerns;
this appears to be a natural division of responsibility and functionality.

% Do Not Reformat!

\begin{tabular}[]{lll}
    \textit{\ATN{}\/}   & \textit{Parser\/} & \textit{Similarity\/}     \\
    Networks            & Algorithm         & Determines the sequence 
                                              of transitions            \\
                        &                   & or actions which 
                                              constitutes a valid       \\
                        &                   & input.                    \\
    Transitions         & Actions           & Save data and impose
                                              conditions the            \\
                        &                   & input must meet to be
                                              considered valid.         \\
    Abbreviations       & Rules             & Responsible for 
                                              classifying input.        \\
\end{tabular}
